---
title: "Publications"
#author:  "[Mathew E Hauer](https://github.com/mathewhauer)"
output:
  html_document:
    fig_width: 1
---

```{r, include = FALSE}
library(tidyverse)
library(scholar)
library(kableExtra)
library(data.table)

id <- "SI0ST5YAAAAJ"
scholar::get_citation_history(id)

a<-scholar::get_publications(id)

pubs <- filter(a, !number == "") %>%
  arrange(-year) %>%
  dplyr::select(-cid)

locs <- tribble(
  ~pubid, ~address, ~altmetric,
  "9yKSN-GCB0IC", '[WEB](http://link.springer.com/article/10.1007/BF03354895) / [PDF](./papers/2013-SpatDemHauer.pdf)', '<div data-badge-popover="right" data-badge-type="donut" data-doi="10.1177/1471082X18801450" data-hide-no-mentions="true" class="altmetric-embed"></div>',
  "d1gkVwhDpl0C", '[WEB](http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0067226) / [PDF](./papers/2013-PlosOneHauer.pdf)', '<div data-badge-popover="right" data-badge-type="donut" data-doi="10.1371/journal.pone.0067226" data-hide-no-mentions="true" class="altmetric-embed"></div>' 
)
pubs <- left_join(pubs, locs)



b <- data.frame("num" = paste0("[",rownames(pubs),"]"), 
                "author" = paste0(pubs$author, '.'," (", pubs$year,'). "' ,pubs$title,'." ', pubs$journal,' ', pubs$number),
                "location" = pubs$address)



names(b) <- c(NULL)


```

```{r include = FALSE, results = "asis"}
kable(b)

```


<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
<style type="text/css">
table.padded-table td { padding:6px; min-width:100px }
</style>


<table class="padded-table">



 <tr><td>[17.]  **Hauer, M.**, Holloway S., & Oda, T. (2020)  "Evacuees and Migrants Exhibit Different Migration Systems after the Great East Japan Earthquake and Tsunami." Forthcoming in *Demography*. </td><td>[WEB](https://link.springer.com/article/10.1007/s13524-020-00883-7) / [PDF](2020-DemographyHauerHollowayOda.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1007/s13524-020-00883-7" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>

 <tr><td>[16.]  **Hauer, M.** & Schmertmann, C. (2020)  "Population pyramids yield accurate estimates of total fertility rates." *Demography*. </td><td>[WEB](https://link.springer.com/article/10.1007/s13524-019-00842-x) / [PDF](./papers/2020-DemographyHauerSchmertmann.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1007/s13524-019-00842-x" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>
 
 <tr><td>[15.]  **Hauer, M.**, Fussell B., Burkett M., Call M., Abel K., Mueller V., McLeman R., Wrathall D. (2020) “Sea-Level Rise and Human Migration.” *Nature Reviews Earth & Environment*. </td><td>[WEB](https://www.nature.com/articles/s43017-019-0002-9) / [PDF](./papers/2019-NREEHauer.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1038/s43017-019-0002-9" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>
 
<tr><td>[14.]  Wrathall D., Mueller V., Clark P., Bell A., Oppenheimer M., **Hauer M.**, Kulp S, Gilmore E.,
Adams H., Kopp R., Abel K., Call M., Chen J., deSherbinin A., Fussell E., Hay C., Jones B.,
Magliocca N., Marino E., Slangen A., and Warner K. (2020) "Meeting the looming policy challenge of
sea-level change and human migration" *Nature Climate Change*. </td><td>[WEB](https://www.nature.com/articles/s41558-019-0640-4) / [PDF](./papers/2019-NCLIMWrathall.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1038/s41558-019-0640-4" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>

 <tr><td>[13.]  **Hauer, M.** & Byars, J. (2019)  "IRS County-to-County Migration Data, 1990-2010." *Demographic Research*. </td><td>[WEB](https://www.demographic-research.org/volumes/vol40/40/default.htm) / [PDF](./papers/2020-DemResHauer.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.4054/DemRes.2019.40.40" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>

 <tr><td>[12.]  **Hauer, M.** (2019)  "Population projections for US counties by age, sex, and race controlled to shared socioeconomic pathway." *Scientific Data*. </td><td>[WEB](https://www.nature.com/articles/sdata20195) / [PDF](./papers/2019-SciDataHauer.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1038/sdata.2019.5" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>

 <tr><td>[11.]  **Hauer, M.** (2019)  "Sociology, Demography, and Economics Presidential Ages and Sex over Time." *Socius*. </td><td>[WEB](https://journals.sagepub.com/doi/abs/10.1177/2378023118825221) / [PDF](./papers/2019-SociusHauer.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1177/2378023118825221" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>

 <tr><td>[10.]  **Hauer, M.**, Hardy, R.D., Mishra, D., & Pippin, J.S. (2019)  "No landward movement: examining 80 years of population migration and shoreline change in Louisiana ." *Population and Environment*. </td><td>[WEB](https://link.springer.com/article/10.1007/s11111-019-00315-8) / [PDF](./papers/2019-PopEnvHauer.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1007/s11111-019-00315-8" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>

 <tr><td>[9.] Schmertmann, C., & **Hauer, M.** (2018)  "Bayesian estimation of total fertility from a population's age–sex structure ." *Statistical Modelling*. </td><td>[WEB](https://journals.sagepub.com/doi/10.1177/1471082X18801450) / [PDF](./papers/2018-StatisticalModelling.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1177/1471082X18801450" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>

 <tr><td>[8.] Hardy, R. D., & **Hauer, M.** (2018) "Social vulnerability projections improve sea-level rise risk assessments." *Applied Geography* 91: 10-20. </td><td>[WEB](https://www.sciencedirect.com/science/article/pii/S0143622817309189) / [PDF](./papers/2018-AppliedGeographerHardyHauer.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="https://doi.org/10.1016/j.apgeog.2017.12.019" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>
  <tr><td>[7.] **Hauer, M.** (2017). "Sea level rise induced migration could reshape the United States population landscape." *Nature Climate Change*  7(5): 321-325.  </td><td>[WEB](http://dx.doi.org/10.1038/nclimate3271) / [PDF](./papers/2017-NCLIMHauerREDUCED.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1038/nclimate3271" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>
  <tr><td>[6.] Shannon, S. & **Hauer, M.** (2017). "A life table approach to estimating disproportionate minority contact in the juvenile justice system." *Justice Quarterly*.  </td><td>[WEB](http://www.tandfonline.com/doi/full/10.1080/07418825.2017.1315163) / [PDF](./papers/2017-JusticeQuarterlyShannonHauer.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1080/07418825.2017.1315163" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>
  <tr><td>[5.] Shannon, J., **Hauer, M.**, Shannon, S., and Weaver, A. (2017). "The Suburbanization of Food Insecurity: An Analysis of Projected     Trends in the Atlanta Metropolitan Area." *Professional Geographer*.  </td><td>[WEB](http://www.tandfonline.com/doi/full/10.1080/00330124.2017.1325751) / [PDF](./papers/2017-ProGeographerShannonHauer.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1080/00330124.2017.1325751" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr> 
   <tr><td>[4.] **Hauer, M.**, Evans, J., and Mishra, D. (2016). "Millions projected to be at risk from sea-level rise in the continental United States.'' *Nature Climate Change* 6(7): 691-695. </td><td> [WEB](http://www.nature.com/nclimate/journal/v6/n7/full/nclimate2961.html) / [PDF](./papers/2016-NCLIMHauer.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1038/nclimate2961" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>  
   <tr><td>[3.] **Hauer, M.**, Evans, J., and Alexander, C. (2015). "Sea-level rise and sub-county population projections in coastal Georgia.''  *Population and Environment* 37(1): 44-62.</td> <td> [WEB](http://link.springer.com/article/10.1007/s11111-015-0233-8) / [PDF](./papers/2015-POENHauer.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1007/s11111-015-0233-8" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr> 
       
 <tr><td>[2.] **Hauer, M.**, Baker, J., and Brown, W., (2013). "Indirect estimates of the total fertility rate using the child  woman/ratio: A comparison with the Bogue-Palmore method.'' *PloS one 8(6)*.</td><td> [WEB](http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0067226) / [PDF](./papers/2013-PlosOneHauer.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1371/journal.pone.0067226" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>        
 <tr><td>[1.] **Hauer, M.**, (2013). "A 3D spatio-temporal geovisualization of subcounty estimates of historic housing density in metro Atlanta, 1940-2009.'' *Spatial Demography* 1(2), 146-161.</td><td> [WEB](http://link.springer.com/article/10.1007/BF03354895) / [PDF](./papers/2013-SpatDemHauer.pdf)</td><td><div data-badge-popover="right" data-badge-type="donut" data-doi="10.1007/BF03354895" data-hide-no-mentions="true" class="altmetric-embed"></div></td></tr>      
  
</table>

----

### Working Papers

**Hauer, M.** & Santos, A. *Climate change could reduce European life expectancy.*  [[PDF]](https://osf.io/preprints/socarxiv/ngtxr)

Keenan, J.M. & **Hauer, M.**. (2020). *Resilience for whom? Demographic change and the redevelopment of the built environment in Puerto Rico.* Forthcoming in Environmental Research Letters.

Landon, CM, Lyles RH, Scrovronick, NC, Abadi, AM, Bilotta R, **Hauer, M.**, Bell, JE, Gribble, MO. (2020). *Mixed-effects negative binomial regression with interval censoring: a simulation study and application to aridity and all-cause mortality among black South Africans over 1997-2013.* Forthcoming in Springer Statistics and Biostatistics.

**Hauer M.**, Saunders, R.K., & Shtob, D. *The Path of Least Resistance Projections of Social Inequalities as a Result of Climate Change in the United States.* [[Preprint]](https://osf.io/preprints/socarxiv/7jtrn/). 

**Hauer M.**, Hardy, R.D., Kulp, S., Mueller, V., Wrathall, D., Clark, P.U., Oppenheimer, M.O. *A framework for classifying and assessing sea level rise risk.* [[Preprint]](https://osf.io/preprints/socarxiv/tf6rj/).

Bell, A., Wrathall, D., Mueller, V., Chen, J., Oppenheimer, M., **Hauer, M.**, Adams, H., Kulp, S., Clark, P., Fussell, E., Magliocca, N., Xiao, T., Gilmore, E., Abel, K., Call, M., Slangen, A. *Simulated migrants move toward vulnerable coastlines in Bangladesh under all sea-level change scenarios through 2100.*

----
