 *Student or Post-Doc.
 
 \begin{etaremune}

    \item Landon, CM, Lyles RH, Scrovronick, NC, Abadi, AM, Bilotta R, \textbf{Hauer, M.}, Bell, JE, Gribble, MO. (2020). "Mixed-effects negative binomial regression with interval censoring: a simulation study and application to aridity and all-cause mortality among black South Africans over 1997-2013." Forthcoming in Springer Statistics and Biostatistics. \\

    \item Keenan, J.M. \& \textbf{Hauer, M.}. (2020). "Resilience for whom? Demographic change and the
redevelopment of the built environment in Puerto Rico." Forthcoming in Environmental Research Letters.

    \item\textbf{Hauer M.} \& Santos A. (2020). "Inaction on climate change projected to reduce European life expectancy." Forthcoming in Population Research and Policy Review \href{https://osf.io/preprints/socarxiv/ngtxr}{[Preprint]}\\  
 
     \item \textbf{Hauer, M.}, Holloway, S., \& Oda, T. (2020). "Evacuees and Migrants Exhibit Different Migration Systems after the Great East Japan Earthquake and Tsunami." \href{https://link.springer.com/article/10.1007/s13524-020-00883-7}{\textit{Demography}}.\\
 
     \item \textbf{Hauer, M.} \& Schmertmann, C. (2020). "Population pyramids yield accurate estimates of total fertility rates." \href{https://link.springer.com/article/10.1007/s13524-019-00842-x}{\textit{Demography} 57: 221-241}.\\
     
     \item \textbf{Hauer M.}, Fussell B., Burkett M., Call M.*, Abel K.*, Mueller V., McLeman R., Wrathall D. (2019). "Sea Level Rise and Human Migration." \href{https://www.nature.com/articles/s43017-019-0002-9}{\textit{Nature Reviews Earth \& Environment} 1-12}.\\

    \item Wrathall D., Mueller V., Clark P., Oppenheimer M., \textbf{Hauer M.}, et al. (2019). "Meeting the looming challenge of future migration from global sea level change." \href{https://www.nature.com/articles/s41558-019-0640-4}{\textit{Nature Climate Change} 9(12): 898-901}. \\
    
    \item \textbf{Hauer, M.}, Byars J*. (2019). "IRS County-to-County Migration Data, 1990-2010." \href{https://www.demographic-research.org/volumes/vol40/40/default.htm}{\textit{Demographic Research} 40: 1153-1166}.

  \item \textbf{Hauer, M.} (2019). "Population projections for US counties by age, sex, and race controlled to shared socioeconomic pathway." \href{https://www.nature.com/articles/sdata20195}{\textit{Scientific Data} 6}.\\
  \hangindent=3.2em\hspace{3em}{\footnotesize * Winner of the 2018 E. Walter Terrie Award from the Southern Demographic Association.}\\
  
   \item \textbf{Hauer, M.} (2019). "Sociology, Demography, and Economics Presidential Ages and Sex over Time." \href{https://journals.sagepub.com/doi/abs/10.1177/2378023118825221}{\textit{Socius} 5}.
 
  \item \textbf{Hauer, M.}, Hardy, R.D.*, Mishra, D., and Pippin, J.S. (2019). "No landward movement: examining 80 years of population migration and shoreline change in Louisiana." \href{https://link.springer.com/article/10.1007/s11111-019-00315-8}{\textit{Population and Environment} 40(4): 369-387}.
 
 \item Schmertmann, C., and \textbf{Hauer, M.} (2018). "Bayesian estimation of total fertility from a population's age-sex structure." \href{https://doi.org/10.1177/1471082X18801450 }{\textit{Statistical Modelling} 19(3): 225-247}.
 
\item Hardy, R. D.*, and \textbf{Hauer, M.} (2018). "Social vulnerability projections improve sea-level rise risk assessments." \href{https://www.sciencedirect.com/science/article/pii/S0143622817309189}{\textit{Applied Geographer} 91: 10-20}.
 
\item Shannon, S. and \textbf{Hauer, M.} (2018). "A life table approach to estimating disproportionate minority contact in the juvenile justice system." \href{http://www.tandfonline.com/doi/full/10.1080/07418825.2017.1315163}{\textit{Justice Quarterly} 35(2): 330-355}.

\item Shannon, J., \textbf{Hauer, M.}, Shannon, S., and Weaver, A. (2018). "The Suburbanization of Food Insecurity: An Analysis of Projected     Trends in the Atlanta Metropolitan Area." \href{http://www.tandfonline.com/doi/full/10.1080/00330124.2017.1325751}{\textit{Professional Geographer} 70(1): 84-93}.

\item \textbf{Hauer, M.} (2017). "Migration induced by sea-level rise could reshape the United States population landscape." \href{http://dx.doi.org/10.1038/nclimate3271}{\textit{Nature Climate Change} 7(5): 321-325}.\\
        \hangindent=3em \hspace{3em}{\footnotesize * Featured in \textbf{over 85 national and international news outlets.}\\
       \hangindent=3.7em \hspace{3em} * The 238th most discussed article out of 250,000+ articles published in 2017 according to \href{https://www.nature.com/articles/nclimate3271/metrics}{Altmetric}.}\\
       
\item \textbf{Hauer, M.}, Evans, J., and Mishra, D. (2016). ``Millions projected to be at risk from sea-level rise in the continental United States.'' \href{http://www.nature.com/nclimate/journal/v6/n7/full/nclimate2961.html}{\textit{Nature Climate Change} 6(7): 691-695}.\\
            \hangindent=3.2em\hspace{3em}{\footnotesize * Winner of the 2014 E. Walter Terrie Award from the Southern Demographic Association.\\
            \hangindent=3.7em\hspace{3em} * Featured in \textbf{over 270 national and international news outlets.}\\
            \hangindent=3.7em\hspace{3em} * The 4th most discussed article published in \textit{Nature Climate Change} in 2016 according to \href{https://twitter.com/NatureClimate/status/814862616770342912}{Altmetric}.\\
            \hangindent=3.7em\hspace{3em} * The 21st most discussed article published on Climate Science in 2016 according to \href{https://www.carbonbrief.org/analysis-climate-papers-featured-media-2016}{Altmetric}.\\
            \hangindent=3.7em\hspace{3em} * The 126th most discussed article out of 277,000+  articles published in 2016 according to \href{https://www.nature.com/nclimate/journal/v6/n7/nclimate2961/metrics}{Altmetric}.}
                
\item \textbf{Hauer, M.}, Evans, J., and Alexander, C. (2015). ``Sea-level rise and sub-county population projections in coastal Georgia.''  \href{http://link.springer.com/article/10.1007/s11111-015-0233-8}{\textit{Population and Environment} 37(1): 44-62}.\\      

\item \textbf{Hauer, M.}, Baker, J., and Brown, W., (2013). ``Indirect estimates of the total fertility rate using the child                        woman/ratio: A comparison with the Bogue-Palmore method.'' \href{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0067226}{\textit{PloS one} 8(6)}.\\

\item \textbf{Hauer, M.}, (2013). ``A 3D spatio-temporal geovisualization of subcounty estimates of historic housing density in metro Atlanta, 1940-2009.'' \href{http://link.springer.com/article/10.1007/BF03354895}{\textit{Spatial Demography} 1(2), 146-161}.\\

 \end{etaremune}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%% In Prep SECTION %%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Under Review}

    \hangindent=2.em \textbf{Hauer M.}, Saunders, R.K., \& Shtob, D. "The Path of Least Resistance Projections of Social Inequalities as a Result of Climate Change in the United States." \href{https://osf.io/preprints/socarxiv/7jtrn/}{[Preprint]}. \\

\hangindent=2.em \textbf{Hauer M.}, Hardy, R.D., Kulp, S., Mueller, V., Wrathall, D., Clark, P.U., Oppenheimer, M.O. "A framework for classifying and assessing sea level rise risk." \href{https://osf.io/preprints/socarxiv/tf6rj/}{[Preprint]}

 \hangindent=2.em Bell, A., Wrathall, D., Mueller, V., Chen, J., Oppenheimer, M., \textbf{Hauer, M.}, Adams, H., Kulp, S., Clark, P., Fussell, E., Magliocca, N., Xiao, T., Gilmore, E., Abel, K., Call, M., Slangen, A. "Simulated migrants move toward vulnerable coastlines in Bangladesh under all sea-level change scenarios through 2100."   

%     
\section{In Prep}

       \hangindent=2.em \textbf{Hauer M.} \& Bohon, S. "Effects without a Cause: The Search for Demographic Anomalies."\\ 
    
%   
%     \hangindent=2.em \textbf{Hauer M.} \& Hardy, RD. "A Unified Conceptual Framework for Sea Level Rise Risk Assessments."\\
%     

    
%    \textbf{Hauer, M.}, Hardy, D. A framework for understanding exposure to sea level rise.\\
  
%    \hangindent=2.em \textbf{Hauer, M.}, Schmertmann, C. High fidelity estimates of subnational total fertility rates.
    
%    \textbf{Hauer, M.}. The spatio-temporal dynamics of county level U.S. fertility, 1930-2010.\\




\section{Commissioned Reports}
\begin{tabularx}{\linewidth}{lX}
2016    & \hangindent=2.em \textbf{Hauer, M.}, and Hensley, E. A New Face of Georgia: An analysis of the state's population projections through 2050. \textit{Governor's Office of Planning and Budget}.\\
2015    & \hangindent=2.em\textbf{Hauer, M.}, Byars, J., Wilson, G., \& Pizarek, M. Transfer Student Report: Demonstrating innovative ways to analyze             student transfer data to answer policy questions. \textit{Board of Regents of the University System of Georgia.}\\
      & \hangindent=2.em\textbf{Hauer, M.}, Lynde, H., Byars, J., Wilson, G., Coyne, J., \& Tanner D. First Time Freshman Report: USG market share and     the Georgia high school to USG pipeline. \textit{Board of Regents of the University System of Georgia.}\\
       & \hangindent=2.em \textbf{Hauer, M.}, Lynde, H., Byars, J., Wilson, G., Coyne, J., \& Tanner, D. Student progression report: Enrollment patterns     that lead to graduation. \textit{Board of Regents of the University System of Georgia.}\\
       & \hangindent=2.em\textbf{Hauer, M.}, Lynde, H., Byars, J. Wilson, G., Coyne, J., \& Tanner, D. University System of Georgia Student Group         Profiles. \textit{Board of Regents of the University System of Georgia.}\\
       & \hangindent=2.em Shannon, J. and \textbf{Hauer, M.} Projections of food insecurity in the metro Atlanta area. \textit{Atlanta Community Food     Bank.}\\
2014     & \hangindent=2.em Evans, J., \textbf{Hauer, M.}, Hardy, D., \& Pippin, S. Assessing social vulnerability using SoVI-Lite: A demonstration study             at Glynn County, GA. \textit{Carl Vinson Institute of Government.}\\
       & \hangindent=2.em Evans, J., Pippin, S., Hardy, D., \& \textbf{Hauer, M.} Social vulnerability and local hazard mitigation planning: Application     and evaluation of SoVI-Lite approach for Glynn County, Georgia. \textit{Carl Vinson Institute of Government.}\\
       & \hangindent=2.em \textbf{Hauer, M.}, A tale of two Georgias: Rural and urban demographic changes in Georgia. \textit{Georgia Healthcare            Foundation.}\\
2012    & \hangindent=2.em \textbf{Hauer, M.} and Vaida, G. Disproportionate minority contact assessment. \textit{Governor's Office of Children and                  Families.}\\
2011   & \hangindent=2.em Tinsley, K. and \textbf{Hauer, M.} Atlama Community Transformation (ACT) district housing assessment. \textit{Glynn County,               GA.}\\
2010    & \hangindent=2.em Clarke, W., Brown, W., \& \textbf{Hauer, M.} The motor use fuel tax in Georgia: Collection efficiency, trends, and                        projections. \textit{MARTA.}\\
       & \hangindent=2.em Clarke, W., Brown, W., \textbf{Hauer, M.}, \& Meyer, M. Metropolitan Atlanta Rapid Transit Authority revenue and expense         forecast evaluation 2011-2016. \textit{MARTA.}\\
      & \hangindent=2.em\textbf{Hauer, M.} Utilizing Census data for non-profits: A training manual for Girls, Inc. \textit{Girls, Inc.}\\
2008    & \hangindent=2.em Simmons, M. and \textbf{Hauer, M.} An analysis and critique of Tallahassee and Leon County transportation funding by                      residential project size. \textit{CNL Real Estate and Development Inc.}\\
2007    & \hangindent=2.em Simmons, M. and \textbf{Hauer, M.} Health and the built environment. \textit{Florida Legislature.}\\
\end{tabularx}

\section{Other}

\textbf{Hauer, M.}. Deviation of PAA President's Age, 1931-2018. \href{http://www.populationassociation.org/wp-content/uploads/PAA-Fall-2017.pdf}{\textit{PAA Affairs}}, 2017